Did COVID-19 Induce A Strenuous Effect on the 311 Non-Emergency Services System?

### 2022-07-17 draft_v2.Rmd
test pretrend

```{r}
summary( felm(data= dat_reg, DAYTOCLOSE~n_allcovid:relevel(factor(date),ref=12)|ZIP+factor(date) ))
```

>>>>

```{r}
#plot coef for pretrend
library(sjPlot)
theme_set(theme_sjplot())
plot_model(lm(data= dat_reg %>% mutate(date = as.factor(date)), DAYTOCLOSE~n_allcovid:relevel(date,ref=11)+n_allcovid+date),
           vline.color = "black",
           title="",
           rm.terms = c("n_allcovid","date [2019-04-01]","date [2019-05-01]","date [2019-06-01]","date [2019-07-01]","date [2019-08-01]","date [2019-09-01]","date [2019-10-01]","date [2019-11-01]","date [2019-12-01]","date [2020-01-01]","date [2020-02-01]","date [2020-03-01]","date [2020-04-01]","date [2020-05-01]","date [2020-06-01]","date [2020-07-01]","date [2020-08-01]"),
           axis.labels = rev(c("Mar 2019","Apr 2019","May 2019", "Jun 2019","Jul 2019","Aug 2019", "Sep 2019","Oct 2019","Nov 2019","Dec 2019","Feb 2020","Mar 2020","Apr 2020","May 2020", "Jun 2020","Jul 2020","Aug 2020"))
           )
